Presentation Title

### 2017-06-12 thesis/chapters/ch1-intro.tex
First draft of protocol overview
(trying to) write some proof

TODO some positive intro about blockchain

One of the key issues in many blockchain systems today is that they are not scalable.
Bitcoin~\cite{bitcoin}, the largest permissionless\footnote{Explain permissionless} blockchain system
in terms of market capitalisation~\cite{bitcoinmarketcap} has a maximum transaction rate of merely 7 transaction per second (TX/s).
This is due to the consensus mechanism in Bitcoin, namely proof-of-work (PoW),
miners can only create new blocks every 10 minutes and every block cannot be larger than 1 megabyte.
Payment processors in use today such as Visa can handle transaction rates in the order of thousands~\cite{visa}.
While Bitcoin may be a revolutionary phenomenon, it clearly cannot be ubiquitous in its current state.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End:

>>>>

\chapter{Introduction}
\label{ch:intro}

Blockchains is one of the most prominent but also controversial technologies of our time.
Never before did we have an incorruptable ledger that can be shared with mutually untrustful parties.
% as long as the majority have a common interest
The ledger in fact can contain any type of data.
Thus enabling applications in myriad of fields,
such as finance~\cite{todo}, heath care~\cite{todo}, logistics~\cite{todo}, energy~\cite{todo} and so on.
However, not everyone is convinced on the practicality of blockchain systems.
Bram Cohen, the inventor of BitTorrent said
``It's getting a lot more media attention than the actual impact it's having so far.''~\cite{cohen}
Forbes listed a few reasons on why we should be skeptical about blockchains~\cite{forbes},
some of them include its accessibility for the layperson and its scalability issues.

Scalability is indeed one of the key challenges we face in blockchain systems today.
Bitcoin~\cite{bitcoin}, the largest permissionless\footnote{Explain permissionless} blockchain system
in terms of market capitalisation~\cite{bitcoinmarketcap} has a maximum transaction rate of merely 7 transaction per second (TX/s).
This is due to the consensus mechanism in Bitcoin, namely proof-of-work (PoW),
miners can only create new blocks every 10 minutes and every block cannot be larger than 1 megabyte.
Payment processors in use today such as Visa can handle transaction rates in the order of thousands~\cite{visa}.
While Bitcoin may be a revolutionary phenomenon, it clearly cannot be ubiquitous in its current state.

@@

### 2017-06-12 thesis/chapters/ch2-model.tex
(trying to) write some proof

\subsubsection*{Asynchronous common subset}
TODO give history/background of ACS
Asynchronous common subset (ACS) is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{enumerate}
    \item \emph{Validity}:
        If any correct party outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ parties.
    \item \emph{Agreement}:
        If a correct party outputs $C$, then every party outputs $C$.
    \item \emph{Totality}:
        If $n - f$ party receive an input, then all correct parties produce an output.
\end{enumerate}

@@

We assume a distributed network where nodes are fully connected,
the channels are reliable\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
},
but messages may be re-ordered and delayed by at most some time $\Delta$,
this is sometimes known as a $\Delta$-synchronous network.
Nodes are identified by their public key thus we assume there exist a Public Key Infrastructure (PKI).
In addition, we assume the existance of cryptographically secure hash function $\textsf{H}(\cdot)$,
that has preimage resistance, second preimage resistance and collision resistance.

@@

For any $r \in \{ x \in \mathbb{Z}_+ : x < \infty \}$, starting at the genesis round (round 0),
the system will eventually reach $r$\textsuperscript{th} round.
Further, for every non-genesis round $r$ ($r > 0$), the following properties must be satisfied.
\begin{enumerate}
    \item \emph{Fair lottery}:
        Every node with a CP block in $\C_{r - 1}$,
        should have an equal probability to be elected as a facilitator in round $r$.
    \item \emph{Consistent facilitators}:
        If one honest node decides on a list of facilitators in round $r$,
        every other node honest decides on the same list.
    \item \emph{Validity}:
        If any correct facilitator outputs a set $C$, then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ facilitators.
        Note that the input is a set of CP blocks, so the output is a set of a set of CP blocks.
    \item \emph{Agreement}:
        If a correct facilitator outputs $C$, then every facilitator outputs $C$.
    \item \emph{Totality}:
        If $n - f$ facilitators receive an input, then all correct facilitators produce an output.
\end{enumerate}
\end{definition}
Note that the final three properties are on the facilitators rather than on every node,
they are the properties ACS. 
The fair lottery and consistent facilitator are properties on every node,
they are prerequites for ACS.

@@

\subsection{Bootstrap Phase}
\label{sec:bootstrap}
Recall that facilitators are computed from the consensus result,
but the consensus result is agreed by the facilitators.
Thus we have a dependency cycle.
The goal of the bootstrap phase is to give us a starting point in the cycle.

@@

\subsection{Setup phase}
The setup phase begins immediately after some consensus result is agreed, but not yet disseminate.
This could be right after the bootstrap phase.
The goal is to reach agreement on a list of new facilitators between every node
and should correspond to the fair lottery and consistent facilitators in \Cref{def:consensus}.

@@

Continuing, upon receiving $\C_{r - 1}$ and at least $t + 1$ valid signatures by $u$, $u$ performs two asks.
First, it computes the new facilitators using $\textsf{get\_facilitator}(C, n)$ (\Cref{alg:facilitator})
and updates its facilitator list to the result.
Second, it creates a new CP block using $\textsf{new\_cp}(\C_{r - 1}, r - 1)$ (\Cref{alg:new-cp}).
This concludes the setup phase.

@@

\subsection{Consensus Phase}
The consensus phase begins after the new facilitators are selected.
Assuming the facilitators are of round $r$,
the goal is to agree on some $\C_r$ between the facilitators.
There are two scenarios in the consensus phase.
First, if node $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h} \rangle$ to all the facilitators.
Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
After $D$ is elapsed, it begins the ACS protocol and some $\C_r$ should be agreed upon by the end of it.
The facilitators must satisfy the validity, agreement and totality properties from \Cref{def:consensus}.
This bring us back to the setup phase and the cycle can be started again.

@@

>>>>

\subsubsection*{Asynchronous common subset}
TODO give history/background of ACS
Asynchronous common subset (ACS) is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{definition}
\label{def:acs}
\begin{enumerate}
    \item \emph{Validity}:
        If any correct party outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ parties.
    \item \emph{Agreement}:
        If a correct party outputs $C$, then every party outputs $C$.
    \item \emph{Totality}:
        If $n - f$ party receive an input, then all correct parties produce an output.
\end{enumerate}
\end{definition}

@@

We assume a distributed network where nodes are fully connected,
the channels are reliable\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
},
but messages may be re-ordered and delayed by at most some time $\Delta$,
this is sometimes known as a $\Delta$-synchronous network.
Nodes are identified by their public key thus we assume there exist a Public Key Infrastructure (PKI).
% TODO everyone has one public key?
Finally, we use the random oracle model, calls to the random oracle are denoted by $\textsf{H}(\cdot)$.

@@

For any $r \in \{ x \in \mathbb{Z}_+ : x < \infty \}$, starting at the genesis round (round 0),
the system will eventually reach $r$\textsuperscript{th} round.
Further, for every non-genesis round $r$ ($r > 0$), the following properties must be satisfied.
% TODO rework this -> agreement, validity, fairness, termination
\begin{enumerate}
    \item \emph{Fair lottery}:
        Every node with a CP block in $\C_{r - 1}$,
        should have an equal probability to be elected as a facilitator in round $r$.
    \item \emph{Consistent facilitators}:
        If one honest node decides on a list of facilitators in round $r$,
        every other node honest decides on the same list.
    \item \emph{Validity}:
        If any correct facilitator outputs a set $C$, then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ facilitators.
        Note that the input is a set of CP blocks, so the output is a set of a set of CP blocks.
    \item \emph{Agreement}:
        If a correct facilitator outputs $C$, then every facilitator outputs $C$.
    \item \emph{Totality}:
        If $n - f$ facilitators receive an input, then all correct facilitators produce an output.
\end{enumerate}
\end{definition}
Note that the final three properties are on the facilitators rather than on every node,
they are the properties ACS. 
The fair lottery and consistent facilitator are properties on every node,
they are prerequites for ACS.

@@

\subsection{Bootstrap Phase}
\label{sec:bootstrap}
% TODO rework this -> bootstrap is simply setting the facilitators in a fair way, no consensus
Recall that facilitators are computed from the consensus result,
but the consensus result is agreed by the facilitators.
Thus we have a dependency cycle.
The goal of the bootstrap phase is to give us a starting point in the cycle.

@@

\subsection{Setup phase}
\label{sec:setup-phase}
% TODO setup phase begins with known facilitators from F_r
The setup phase begins immediately after some consensus result is agreed, but not yet disseminate.
This could be right after the bootstrap phase.
The goal is to reach agreement on a list of new facilitators between every node
and should correspond to the fair lottery and consistent facilitators in \Cref{def:consensus}.

@@

Continuing, upon receiving $\C_{r - 1}$ and at least $n - f$ valid signatures by $u$, $u$ performs two asks.
First, it computes the new facilitators using $\textsf{get\_facilitator}(C, n)$ (\Cref{alg:facilitator})
and updates its facilitator list to the result.
Second, it creates a new CP block using $\textsf{new\_cp}(\C_{r - 1}, r - 1)$ (\Cref{alg:new-cp}).
This concludes the setup phase.

@@

\subsection{Consensus Phase}
\label{sec:consensus-phase}
The consensus phase begins after the new facilitators are selected.
Assuming the facilitators are of round $r$,
the goal is to agree on some $\C_r$ between the facilitators.
There are two scenarios in the consensus phase.
First, if node $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h} \rangle$ to all the facilitators.
Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
After $D$ is elapsed, it begins the ACS protocol and some $\C_r$ should be agreed upon by the end of it.
The facilitators must satisfy the validity, agreement and totality properties from \Cref{def:consensus}.
This bring us back to the setup phase and the cycle can be started again.

@@

% TODO consensus phase ends when F_{r + 1} is selected
% TODO remove duplicate CP blocks

### 2017-06-12 thesis/chapters/ch3-analysis.tex
(trying to) write some proof

\section{Correctness}
Our objective in this section is to establish correctness,
in particular our system should have the properties described in \Cref{def:consensus}.

We first give the proof outline.

Three aspects:
checkpoints (consensus)
    for every round we need fair lottery, consistent facilitators, agreement, total order, liveness
    for the whole thing, we need global liveness
transactions (tamperproofness)
    implicit consensus on transactions
    maintain chain structure (not possible, but we can do it probabilistically)

>>>>

\section{Correctness}
Our first objective in this section is to establish truths regarding the correctness of our protocol.
We do this in two parts.
First we use mathematical induction to show that properties in \Cref{def:consensus} holds for all round.
Building on top that, if \Cref{def:consensus} is true, then we can show that many properties in \Cref{def:validation} is true.

\textbf{\emph{Correctness of consensus}}

$\forall r \in \mathbb{N}$, the following properties must be satisfied.
\begin{enumerate}
    \item \emph{Agreement}:
        If one honest node outputs a list of facilitators $F_r$,
        every other node honest decides on $F_r$
    \item \emph{Validity}:
        If any honest node outputs $F_r$, then $|F_r| > n$ and $|F_r|$ must contain at least $n - t$ honest nodes.
    \item \emph{Fairness}:
        Every node should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        At the end of the round, every node outputs some $F_r$.
\end{enumerate}

\subsection{Correctness of Consensus}

We begin our analysis by establishing the fact that the $\textsf{get\_facilitator}(\cdot)$ is fair.
\begin{lemma}
\label{lemma:fairness}
\textbf{\emph{Fairness of facilitator election}}

Every node with a CP block in $\C_r$, should have an equal probability to be elected as a facilitator.
\end{lemma}
\begin{proof}
This directly follows from the random oracle model.
Recall that the luck value is computed using $\textsf{H}(\C_r, || pk_i)$.
Since $pk_i$ is unique for every node that has a CP block in $\C_r$, the output of $\textsf{H}(\cdot)$ is uniformly random.
This implies that the ordered sequence by luck value is uniformly random.
\end{proof}

Using \Cref{lemma:fairness}, we show that our consensus protocol satisfied \Cref{def:consensus}.
\begin{lemma}
\textbf{\emph{Correctness of consensus}}
$\forall r \in \mathbb{N}$, agreement, validity, fairness and termination holds.
\end{lemma}

\begin{proof}
We proof by mathematical induction.

In the base case, agreement, validity fairness and termination follows directly from the bootstrap protocol, due to the bootstrap oracle.
Note that the result is $F_1$, which indicates the facilitators that are agreed in round 1 and are responsible for driving the ACS protocol in round 2.

For the inductive step, we assume that the properties hold for round $r$.
Then, to start round $r + 1$, the honest nodes begin sending CP blocks to $F_r$. % TODO but they don't send at the same time!
Since the honest region in $F_r$ waits for $D$ and $D \gg \Delta$,
the CP blocks of the honest nodes are guaranteed to be received by at least $n - t$ facilitators.
The agreement property of ACS (from \Cref{def:acs}) ensures that the consensus result $\C_{r + 1}$ is in consensus. 
The validity property of ACS ensures that $\C_{r + 1}$ contains the input of at least $n - 2t$ parties, but this is a quorum containing at least one honest facilitator,
thus $\C_{r + 1}$ contains the CP blocks of all facilitators.
Observe that $F_{r + 1}$ is computed using the deterministic function $\textsf{get\_facilitators}(\cdot)$.
Thus agreement of $F_{r + 1}$ follows directly from agreement of ACS.
Due to the assumption that the adversary cannot corrupt more than $t$ nodes,
validity of $F_{r + 1}$ also follows from validity of ACS.
The fairness property follows from \Cref{lemma:fairness}.
Finally, the termination property holds because $D$ eventually elapses and then ACS eventually terminates.
This completes our proof.

\end{proof}

\subsection{Correctness of Validation}

Remark: chain structure cannot be satisfied, but can be probabilistically checked
